### 2024-04-07 texts/paper_closing.tex
decide on regional density specification (count + count-popm interaction)
aslo add predicted avg hazard for different proxcnt10/popm_circle10 situations

% Created 2024-04-04 do 20:38
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Thu Apr  4 20:37:25 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 275 & 0.574 &  0.593 &  0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.159 &  0.169 &  0.37 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.267 &  0.238 &  0.43 & 0 & 1 \\ 
   & Founder died & 58 & 0.121 &  0.098 &  0.30 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 178 & 0.372 &  0.410 &  0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 &  0.189 &  0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &  0.140 &  0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.263 &  0.261 &  0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 229 & 0.478 &  0.488 &  0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 &  0.304 &  0.46 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  &  0.797 &  0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  &  0.150 &  0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  &  0.054 &  0.23 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density &  &  & 20.889 & 18.49 & 1 & 62 \\ 
   & Pop. (millions) within 10km &  &  &  1.378 &  1.74 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  &  2.707 &  2.99 & 1 & 16 \\ 
   & Europe and North America & 312 & 0.651 &  0.645 &  0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 &  0.012 &  0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.267 &  0.282 &  0.45 & 0 & 1 \\ 
   & Region - Europe & 241 & 0.503 &  0.501 &  0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 &  0.042 &  0.20 & 0 & 1 \\ 
   & Region - North America & 71 & 0.148 &  0.143 &  0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 &  0.019 &  0.14 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Thu Apr  4 20:37:33 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_more}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .20 \; (0.36) \\ 
   & Gender - Couple & .12 \; (0.37) \\ 
   & Founder died & .21 \; (0.54) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .84 \; (0.48) \\ 
   & Self-Identification - Collection & .46 \; (0.58) \\ 
   & Self-Identification - Other & 1.34 \; (0.38)^{***} \\ 
   & AN Ranking - Included & .64 \; (0.38) \\ 
   & AN Ranking - Dropped & .87 \; (0.53) \\ 
   & Founder name in Museum name & -.27 \; (0.33) \\ 
   & MOW inclusion & -.84 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density & -.05 \; (0.03) \\ 
   & PM density$^{2}$ & .00 \; (0.00) \\ 
   & Pop. (millions) within 10km & .02 \; (0.11) \\ 
   & Nbr PM within 10km & .12 \; (0.06)^{*} \\ 
   \hline
 & Museum-years & 6423 \\ 
   & Closures & 52 \\ 
   & log. Likelihood & -257.05 \\ 
   & AIC & 542.09 \\ 
   & BIC & 569.41 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

>>>>

% Created 2024-04-07 zo 14:03
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Sun Apr  7 12:05:30 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 275 & 0.574 &   0.593 &   0.49 & 0 & 1 \\ 
   & Gender - Female & 76 & 0.159 &   0.169 &   0.37 & 0 & 1 \\ 
   & Gender - Couple & 128 & 0.267 &   0.238 &   0.43 & 0 & 1 \\ 
   & Founder died & 58 & 0.121 &   0.098 &   0.30 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 178 & 0.372 &   0.410 &   0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 101 & 0.211 &   0.189 &   0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 74 & 0.154 &   0.140 &   0.35 & 0 & 1 \\ 
   & Self-Identification - Other & 126 & 0.263 &   0.261 &   0.44 & 0 & 1 \\ 
   & Founder name in Museum name & 229 & 0.478 &   0.488 &   0.50 & 0 & 1 \\ 
   & MOW inclusion & 91 & 0.190 &   0.304 &   0.46 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  &   0.797 &   0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  &   0.150 &   0.36 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  &   0.054 &   0.23 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  &   0.411 &   1.23 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  &   1.322 &   1.69 & 0.000087 & 10.81 \\ 
   & Pop. (millions) country &  &  & 156.197 & 287.82 & 0.037 & 1412.36 \\ 
   & Nbr PM within 10km &  &  &   1.601 &   2.97 & 0 & 15 \\ 
   & PM density (10km) &  &  &   1.423 &   4.01 & 0 & 41.85 \\ 
   & Europe and North America & 312 & 0.651 &   0.645 &   0.48 & 0 & 1 \\ 
   & Region - Africa & 7 & 0.015 &   0.012 &   0.11 & 0 & 1 \\ 
   & Region - Asia & 128 & 0.267 &   0.282 &   0.45 & 0 & 1 \\ 
   & Region - Europe & 241 & 0.503 &   0.501 &   0.50 & 0 & 1 \\ 
   & Region - Latin America & 22 & 0.046 &   0.042 &   0.20 & 0 & 1 \\ 
   & Region - North America & 71 & 0.148 &   0.143 &   0.35 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.021 &   0.019 &   0.14 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Sun Apr  7 12:05:38 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & .22 \; (0.37) \\ 
   & Gender - Couple & .14 \; (0.36) \\ 
   & Founder died & .28 \; (0.53) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .71 \; (0.48) \\ 
   & Self-Identification - Collection & .14 \; (0.59) \\ 
   & Self-Identification - Other & 1.32 \; (0.38)^{***} \\ 
   & AN Ranking - Included & .50 \; (0.38) \\ 
   & AN Ranking - Dropped & .82 \; (0.52) \\ 
   & Founder name in Museum name & -.35 \; (0.33) \\ 
   & MOW inclusion & -.90 \; (0.40)^{*} \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .56 \; (0.42) \\ 
   & PM density$^{2}$ (country) & -.02 \; (0.02) \\ 
   & Pop. (millions) within 10km & .29 \; (0.11)^{**} \\ 
   & Nbr PM within 10km & .30 \; (0.09)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.10 \; (0.04)^{**} \\ 
   \hline
 & Museum-years & 6423 \\ 
   & Closures & 52 \\ 
   & log. Likelihood & -253.41 \\ 
   & AIC & 536.82 \\ 
   & BIC & 566.09 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}}
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}
